### 2012-12-07 counterexample to bratman on shared intention/a counterexample to bratman on shared intention.tex
working on it

The first contrast case, Gilbert's, shows that the difference can’t be just  a matter of coordination because people who are merely happen to be walking side by side each other also need to coordinate their actions in order to avoid colliding.  
Note also that in both cases each individual's walking is intentional, so our intentionally walking together cannot be  only a matter of our each intentionally walking.
The second contrast case, Searle's, shows that the difference can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too.%
\footnote{
This use of contrast cases resembles \citet{Pears:1971fk}: he uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents. 
} 
Perhaps, then, a notion of shared intention is needed to distinguish the two cases.  
Perhaps it is our acting on a shared intention that we walk together which distinguishes us from two strangers who happen to be walking side by side.%
\footnote{
Many philosophers agree that a notion of shared intention is useful for understanding acting together. 
Compare \citet[p.\ 5]{Gilbert:2006wr}: `I take a collective action to involve a collective intention.'  See also  
	\citet[p.\ 381]{Carpenter:2009wq}, 
	\citet[p.\ 369]{Call:2009fk}, 
	\citet{Kutz:2000si}, 
	\citet[p.\ 117]{rakoczy_pretend_2006} and 
	\citet{Tollefsen:2005vh}.
	}

@@

Before going further we must distinguish two versions of the claim that (1)--(3) are collectively sufficient for shared intention.
The \emph{weak claim} is that there is some J such that these conditions are sufficient for you and I to intend that we J.
The \emph{strong claim} is that for any J, these conditions are sufficient for you and I to intend that we J. 
Our initial counterexample will be directed to the strong claim.
However, after we have constructed this counterexample it will become clear that there are also counterexamples involving a wide range mundane activities to which Bratman explicitly takes his account to apply.
Even walking together%
	\footnote{
	See \citet[p.\ 150]{Bratman:2009lv}.
	}
	%
and painting a house together%
	\footnote{
	See \citet[p.\ 331]{Bratman:1992mi}.
	}
	%
can serve as counterexamples.
%One of Bratman's aims is to show that an account of shared intention should be \emph{conceptually conservative}.
%He aims, that is, to show that  it is possible to give an account of shared intention using only concepts that `are available within the theory of individual planning agency' \citep[p.\ 163]{Bratman:2009lv}.  
%Achieving this aim would require the strong claim, and it is to the strong claim that our counterexample is directed.%
%\footnote{
%We do not aim to attack the claim that it is possible to give a conceptually conservative account of shared intention. 
%The point we are making here is just that if an account
%}

How could we show that our meeting Bratman's conditions, (1)--(3), is not in fact sufficient for us to have a shared intention? 
We seek a case where the conditions are met although we lack a shared intention.
But how could we determine that we lack a shared intention?
As already mentioned, the notion of shared intention is supposed to 
	make it possible to 
	characterise systematically a difference between 
		cases involving shared agency (such as our walking together)
		and
		cases involving only parallel  individual agency (such as two strangers who happen to be walking the same route side-by-side). 
Suppose, then, that we had a trio of cases, A, B and C, each involving two agents.
Suppose, further, that A and B involved parallel agency only, whereas C involved shared agency.
Then we could be sure that A and B do not involve shared intention.
Now suppose 
	that, for some relevant J, Bratman's conditions, (1)--(3) above, were met in cases B and C alike, 
	that in each case the structure of intention and knowledge played an appropriate role in guiding the agents' actions,
	and that in each case the agents thereby successfully J.
Then case B would be our counterexample:
Bratman's conditions are met but there is no shared intention.
This is how our counterexample will work.
(Strictly speaking, case A is not necessary; but including it simplifies exposition.)

@@

To illustrate, first consider Bratman's `mafia case' where two people go to New York together by virtue of one of them forcing the other into a car and driving off \citep[p.\ 333]{Bratman:1992mi}. 
Next consider a paradigm case of where two friends cooperatively go to New York together.
It's possible to conceive of an act type of going to New York together which is broad enough that both cases, the coercive and the cooperative, fall under it.
And it's even possible to desire or intend to be involved in an act of this type.
A gangster might intend to go to New York with a future victim without having yet decided whether they will do this cooperatively or coercively.

@@

\section{Unshared Intentions}
As a further preliminary we need to introduce a definition.
Let us stipulate that we have an \emph{unshared intention} that we <J$_1$, J$_2$> where J$_1$$\neq$J$_2$ just if:
%
\begin{quote}
\label{df:unshared_intention}
1$^\prime$. (a) I intend that we J$_1$ and (b) you intend that we J$_2$

@@

Consider the possibility of one player intending, unilaterally, that the two players do something.
Suppose that one of the players---Ayesha, say---can knowledgeably predict that if she performs a certain sequence actions, <a$_1$, a$_2$, ...\ a$_n$>, then Ahmed will simultaneously perform certain other actions, <b$_1$, b$_2$, ...\ b$_n$>,
 and the upshot will be that the cross hits the red square.
Were this to happen, it would be true that Ayesha and Ahmed made the cross hit the red square.
Suppose, further, that Ayesha can intend to perform those actions <a$_1$, a$_2$, ...\ a$_n$>.
Then Ayesha can intend, unilaterally, that they, Ayesha and Ahmed, make the cross hit the red square (see Section \vref{sec:netural_wrt_shared_intentionality}).

@@

This is not quite enough to meet the second condition, (2), because there is also a requirement about meshing subplans. 
To apply this requirement we need to generalise Bratman's definition of meshing:
\begin{quote}
`our individual subplans concerning our J-ing \emph{mesh} just in case there is some way we could J that would not violate either of our subplans but would, rather, involve the successful execution of those subplans' \citep[p.\ 106]{Bratman:1993je}.
\end{quote}
A natural generalisation is this:
\begin{quote}
our individual subplans concerning our <J$_1$, J$_2$>-ing \emph{mesh} just in case there is some way I could J$_1$ and you could J$_2$ that would not violate either of our subplans but would, rather, involve the successful execution of those subplans. 
\end{quote}
%
To illustrate, 
their subplans would fail to mesh if, in intending that they make the cross hit the red square,  Ayesha's plans had included pushing Ahmed out of the way and seizing his controls. 
They would also fail to mesh if Ayesha were planning to trick Ahmed into a situation where we would be unable to perform the actions he had been planning.
But in the case we have been describing, the agents subplans mesh perfectly.
Each agent's subplans involve manipulating his or her own controls,
and the successes each seeks in doing this depends on the other successfully carrying out their subplans.
So Ayesha can rationally intend that they, Ayesha and Ahmed, make the cross hit the red square in accordance with and because of their intentions and meshing subplans of them.
And Ahmed likewise for making the cross hit the blue circle.

@@

In the situation just described,
Ayesha and Ahmed are playing a game and have different tasks.
Thanks to special features of the game environment, they both succeed by acting on an unshared intention.
Now compare two further players, Beatrice and Baldric, who are playing the same game. 
Their situations, knowledge states, intentions and actions are as similar as possible to Ayesha's and Ahmed's except for one detail.
Just by chance they have been assigned identical tasks: Beatrice's task is to make the cross hit the red square and Baldric's task is the same.
So where Ayesha and Ahmed have an unshared intention that they <J$_1$, J$_2$>,
Beatrice and Baldric meet Bratman's conditions (1)--(3) for having a shared intention that they J$_1$.  
But Beatrice, in planning and acting, does not rely on the coincidence of their intentions; and nor does Baldric.
(Beatrice relies on the fact Baldric intends that they J$_1$, of course; but she does not rely on the fact that Baldric intends what she intends.)
Furthermore, due to an artefact of the way the game is structured,
the unshared intention and the 
	Bratman intention 
	\label{df:bratman_intention}
	(as we might label the structure of intention and knowledge while leaving open whether it constitutes a shared intention), result in the two pairs performing same actions in the same way.
That is, Beatrice reasons about Baldric much as Ayesha reasons about Ahmed and Beatrice and does what Ayesha does, and likewise for Baldric and Ahmed.

We claim that Beatrice and Baldric have a shared intention that they J$_1$
only if 
Ayesha and Ahmed have a shared intention.%
\footnote{
Strictly speaking, 
	what matters for our argument is whether Ayesha and Ahmed have a shared intention \emph{in virtue of having the unshared intention that they <J$_1$, J$_2$>}.
	This is because, strictly speaking, we need to show, not that Beatrice and Baldric lack any shared intention whatsoever, but only that they lack a shared intention that they J$_1$ just in virtue of meeting Bratman's conditions (see (1)--(3) on page  \pageref{quote:bratman_account}). 
	For ease of exposition this is not made explicit in the main text.
} 
This claim follows from the similarities of the two cases.
The only difference is that Beatrice and Baldric happen to be assigned the same task, whereas Ayesha and Ahmed are not.
And neither Beatrice nor Baldric makes use of the fact that they have the same task. 
(This is not due to ignorance: it's just how they choose to approach their tasks.)
So if we consider on how  
		the case of Beatrice and Baldric
	differs from
		 that of Ayesha and Ahmed,
we can see that these differences do not plausibly amount to a difference with respect to shared agency.
Shared intention cannot feature in one case but not the other.

To show that Beatrice and Baldric do not have a shared intention it remains only for us to show that Ayesha and Ahmed do not have one. 
Here we must be careful.
First note that,
	 since Bratman provides only sufficient conditions for shared intention, 
	 his account doesn't tell us that an unshared intention is not a shared intention.
For all Bratman says, the conditions defining unshared intention might  be sufficient for shared intention.

But doesn't shared intention require at least this much,
that there be a single activity  about which each the agent involved has an intention? 
This might reasonably be doubted by those who, like Bratman, reject the Simple View according to which when an individual intentionally F-s she has an intention concerning her F-ing \citep{Bratman:1984jr}.
So 
	we shall not infer  that Ayesha and Ahmed lack a shared intention
	just because (by construction) there is no F such that Ayesha and Ahmed each intend that they, Ayesha and Ahmed, F.

Can we then appeal directly to intuition to show that Ayesha and Ahmed lack a shared intention?
Ayesha sees Ahmed's actions as constraints on her own, or else as opportunities.
She exploits Ahmed's intentions for her own ends.
Of course the situation is reciprocal: Ahmed exploits Ayesha in equal measure.
Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
and this is the full extent of their cooperation. 
We don't suppose that reciprocal exploitation is incompatible with shared intention. 
But Ayesha and Ahmed's interaction consists entirely in this sort reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.
Perhaps it is clear enough that 
the sort of shared agency that an account of shared intention is supposed to capture must involve more than this. 
If so, we can already claim that Ayesha and Ahmed are not acting on a shared intention.
But philosophers' intuitions about shared agency may not be entirely, so it would be better if we could avoid such a blunt appeal to intuition.

How else could we support the claim that Beatrice and Baldric lack a shared intention? 
As mentioned at the start, 
the contrast cases are often used to anchor intuitions in theorising about shared agency.
In the next section we shall further support our claim by contrasting Beatrice and Baldric's case with a further case, one which is as similar as possible and which does seem to involve shared agency.
The fact that Beatrice and Baldric's case contrasts with this new case will support the claim that Beatrice and Baldric lack shared intention.
This is the aim of the following section.
A first motive for introducing this new contrast case is that it provides an indication concerning what is missing from Bratman's account, and so may help us to understand why his conditions are not sufficient for shared intention.

@@

First we need to introduce the notion of an agent-neutral plan.
We stipulate that a planning process, or a plan, is \emph{agent-neutral} just if it does not involve identifying any particular agents.  
This sort of planning is quite common.
For example, some housemates who have decided to take on an allotment to grow vegetables might sit down together to plan what needs doing without yet assigning roles to particular individuals. 
In so planning, each housemate is thinking about what is to be done and not what she herself will do.  
%(This is an idealisation, of course.)
At some point the housemates stop planning.
(This does not necessarily mean that they have a fully worked out plan; like any other plans, agent-neutral plans can have gaps that may need filling in later.)
They now divide up the roles.
Of course they may not find a way of dividing up roles that everyone is prepared to go along with---individuals' preferences, abilities and intentions may block the plan's adoption.
But suppose the housemates do divide up the roles in a way that is acceptable to everyone, 
	and that each implements her part in the plan.
Then each conceives of her own and the others' actions as part of single plan directed to achieving a single outcome.

In the above example of agent-neutral planning,
	the housemates plan together and agree on a common plan.
	Planning together is plausibly an activity which involves shared agency.
	Note, however, that an individual can construct an agent-neutral plan by herself, even if its eventual execution will involve others.
	In fact, two or more individuals who are assigned a task might each individually engage in agent-neutral planning in parallel.
	The task demands and their planning strategies may conspire to ensure that they each come up with the same agent-neutral plan.
	The task demands and manifest properties of the agents, such as their distribution in space, may also ensure that each agent also assigns the same roles to the same individuals.
(Strictly speaking it is not necessary for the plans and role assignments to be identical; it is enough if the resulting agent-specifying plans are, in a special sense, compatible.%
\footnote{
\label{fn:df_compatible}
Suppose that, for some outcome, two or more agents each have a plan for the realisation of that outcome. 
(These plans may, but need not, specify roles for all of the agents; but the plans must be agent-specific, not agent-neutral.)
By saying that these plans are \emph{compatible} we mean that:
(i) 
no agent would normally be prevented from performing the role she is assigned in her own plan by other agents performing the roles they are assigned in their plans;
and
(ii)
if all facts about which agents have which roles in which plans were common knowledge to the agents,
this would not affect the rationality of their each acting on the intention that they realise the outcome by performing the role she is assigned in her own plan.
%	each agent could rationally act on the intention that they realise the outcome by performing the role she is assigned in her own plan,
%	and she could do so even if all facts about which agents are performing which roles in which plans were common knowledge to the agents.
To illustrate, suppose that our task is to press a button simultaneously. 
If your plan is that each of us will to start to move in exactly 60 seconds and press the button 5 seconds later whereas my plan specifies that you are the leader and we are each to press the button 5 seconds after you start moving, then our plans are compatible.
})
%
Finally, each agent may know enough about herself and the others to be able to determine, without communicating, whether the plan and role assignments will be acceptable to everyone. 
	And all of this---that they engage in parallel, agent-neutral planning resulting in identical (or compatible) plans and role assignments, which are acceptable to all---may be common knowledge to the agents.
	So it is possible, in principle at least, 
	that several agents might each individually engage in agent-neutral planning and rationally perform their part in the resulting plan, knowing that the others will do likewise.
	Parallel, agent-neutral planning can rationally result in coordinated action without presupposing shared agency.%
\footnote{
Note that we are claiming only that shared agency is not presupposed.
Our view is consistent with (but does not depend on) the claim
that
	if some agents each engage in parallel, agent-neutral planning and then rationally perform their part in the resulting plan,
	the upshot would be an exercise of shared agency.
}

Different perspectives are involved in
	forming a plan for  your own actions  only
and 
	forming a plan for  your own and others actions.
%\footnote{
%Perhaps it is impossible, strictly speaking, to plan others' actions. 
%In speaking loosely about planning your own and others actions, we mean the activity of constructing an agent-neutral plan and assigning roles as described above.
%}
  Of course, in planning your only your own actions, it may be necessary to consider how others' actions will affect, and be affected by, your won.
But in this case, the others' actions feature in your planning as constraints and opportunities.
By contrast, forming a plan for your own and others' actions 
	involves conceiving of your own and the others' actions as elements in a single plan directed to a single outcome.

@@

In short, then, Caitlin and Ciaran are like Beatrice and Baldric in nearly every respect. 
Each pair has a Bratman intention that they J$_1$,%
\footnote{
As stipulated above (see page \pageref*{df:bratman_intention}), 
two agents have a \emph{Bratman intention} that they J just if they meet conditions (1)--(3) on page \pageref{quote:bratman_account}.
}
%
 each pair acts on this intention and each pair ends up performing the same sequence of actions.
The difference is just that Beatrice and Baldric make no use of the fact that they are performing the same task.
	This fact does not show up in their planning. 
	Rather, each plans her own actions only and treats the other's actions as constraints to work around or opportunities to exploit.
By contrast, Caitlin and Ciaran embrace the fact that they are performing the same task. 
They may not like having to act together; in fact each may far prefer to act alone were that possible.
And, like Beatrice and Baldric, they are unconcerned with each other's success except insofar as their own success depends on it.
But Caitlin and Ciaran nevertheless make use of the fact that they have to perform a single task together by each constructing a single plan covering both of their actions and then carrying out their parts in these plans.
So why does Caitlin and Ciaran's case, but not Beatrice and Baldric's, plausibly involve shared agency?
The reason is  this:
	 at some stage of the planning which rationally guides and coordinates their actions,
	Caitlin and Ciaran each conceive of their actions as part of a single plan directed to achieving a single outcome.

Given the way Beatrice and Baldric's case contrasts with Caitlin and Ciaran's,
we conclude that Beatrice and Baldric do not have a shared intention.
But, by construction, 
 Beatrice and Baldric do meet Bratman's conditions for shared intention, and they do act appropriately on the corresponding intentions and knowledge. 
 So Beatrice and Baldric's case  is a counterexample to sufficiency of Bratman's conditions for shared intention (see (1)--(3) on page \pageref{quote:bratman_account}).

In describing Caitlin and Ciaran we have not introduced contralateral commitments or other elements foreign to Bratman's account of shared agency. 
Our counterexample draws on the same planning resources Bratman's account draws on, with just one addition.
The addition is the idea that agents can conceive, or fail to conceive, of their actions as part of a single plan. 
In at least some cases, shared agency differs from individual agency in part because shared agency involves changing perspective so that one’s own and other’s actions are conceived of as parts of a single plan.

>>>>

The first contrast case, Gilbert's, shows that the difference can’t be just  a matter of coordination because people who merely happen to be walking side by side each other also need to coordinate their actions in order to avoid colliding.  
Note also that in both cases each individual's walking is intentional, so our intentionally walking together cannot be  only a matter of our each intentionally walking.
The second contrast case, Searle's, shows that the difference can’t just be that the resulting actions have a common effect because merely parallel actions can have common effects too.%
\footnote{
This use of contrast cases resembles \citet{Pears:1971fk}: he uses contrast cases to argue that whether something is an ordinary, individual action depends on its antecedents. 
} 
Perhaps, then, a notion of shared intention is needed to distinguish the two cases.  
Perhaps it is our acting on a shared intention that we walk together which distinguishes us from two strangers who happen to be walking side by side.%
\footnote{
Many philosophers hold that a notion of shared intention is useful for understanding acting together. 
Compare \citet[p.\ 5]{Gilbert:2006wr}: `I take a collective action to involve a collective intention.'  See also  
	\citet[p.\ 381]{Carpenter:2009wq}, 
	\citet[p.\ 369]{Call:2009fk}, 
	\citet{Kutz:2000si}, 
	\citet[p.\ 117]{rakoczy_pretend_2006} and 
	\citet{Tollefsen:2005vh}.
	}

@@

Before going further we must distinguish two versions of the claim that (1)--(3) are collectively sufficient for shared intention.
The \emph{weak claim} is that there is some J such that these conditions are sufficient for you and I to intend that we J.
The \emph{strong claim\label{strong_claim}} is that for any J, these conditions are sufficient for you and I to intend that we J. 
Our initial counterexample will be directed to the strong claim.
However, after we have constructed this counterexample it will become clear that there are also counterexamples involving a wide range mundane activities to which Bratman explicitly takes his account to apply.
Even walking together%
	\footnote{
	See \citet[p.\ 150]{Bratman:2009lv}.
	}
	%
and painting a house together%
	\footnote{
	See \citet[p.\ 331]{Bratman:1992mi}.
	}
	%
can serve as counterexamples.
%One of Bratman's aims is to show that an account of shared intention should be \emph{conceptually conservative}.
%He aims, that is, to show that  it is possible to give an account of shared intention using only concepts that `are available within the theory of individual planning agency' \citep[p.\ 163]{Bratman:2009lv}.  
%Achieving this aim would require the strong claim, and it is to the strong claim that our counterexample is directed.%
%\footnote{
%We do not aim to attack the claim that it is possible to give a conceptually conservative account of shared intention. 
%The point we are making here is just that if an account
%}

To show that  Bratman's conditions, (1)--(3), are not in fact sufficient for shared intention we need 
a case where the conditions are met and we lack a shared intention.
But how could we determine that we lack a shared intention?
As already mentioned, the notion of shared intention is supposed to 
	make it possible to 
	characterise systematically a difference between 
		cases involving shared agency (such as our walking together)
		and
		cases involving only parallel  individual agency (such as two strangers who happen to be walking the same route side-by-side). 
Suppose, then, that we had a trio of cases, A, B and C, each involving two agents.
Suppose, further, that A and B involved parallel agency only, whereas C involved shared agency.
Then we could be sure that A and B do not involve shared intention.
Now suppose 
	that, for some J, Bratman's conditions, (1)--(3) above, were met in cases B and C alike.
Suppose also that in each case, B and C, the structure of intention and knowledge mention specified by Bratman's conditions 
 played an appropriate role in guiding the agents' actions,
	and that in each case the agents did thereby  successfully J.
Finally, suppose that cases A, B and C are as similar as possible except for the differences mentioned.
Then case B would be our counterexample:
Bratman's conditions are met but there is no shared intention.
This is how our counterexample will work.
(Strictly speaking, case A is not necessary; but including it simplifies exposition.)

@@

To illustrate, first consider Bratman's `mafia case' where two people go to New York together by virtue of one of them forcing the other into a car and driving off \citep[p.\ 333]{Bratman:1992mi}. 
Next consider a paradigm case of where two friends cooperatively go to New York together.
It's possible to conceive of an act type of going to New York together which is broad enough that both cases, the coercive and the cooperative, fall under it.
And it's even possible to desire or intend to be involved in an act of this type.
A gangster might intend to go to New York with someone without having yet decided whether they will do this cooperatively or coercively.

@@

\section{Unshared Intentions}
\label{sec:unshared_intentions}
As a further preliminary we need to introduce a definition.
Let us stipulate that we have an \emph{unshared intention} that we <J$_1$, J$_2$> where J$_1$$\neq$J$_2$ just if:
%
\begin{quote}
\label{df:unshared_intention}
1$^\prime$. (a) I intend that we J$_1$ and (b) you intend that we J$_2$

@@

Consider the possibility of one player intending, unilaterally, that the two players do something.
Suppose that one of the players---Ayesha, say---can knowledgeably predict that if she performs a certain sequence of actions, <a$_1$, a$_2$, ...\ a$_n$>, then Ahmed will simultaneously perform certain other actions, <b$_1$, b$_2$, ...\ b$_n$>,
 and the upshot will be that the cross hits the red square.
Were this to happen, it would be true that Ayesha and Ahmed made the cross hit the red square.
Suppose, further, that Ayesha can intend to perform those actions <a$_1$, a$_2$, ...\ a$_n$>.
Then Ayesha can intend, unilaterally, that they, Ayesha and Ahmed, make the cross hit the red square.
(This intention concerns an action conceived of as neutral with respect to shared intentionality; see  Section \vref{sec:netural_wrt_shared_intentionality}).

@@

This is not quite enough to meet the second condition, (2), because there is also a requirement about meshing subplans. 
To apply this requirement we need to generalise Bratman's definition of meshing:
\begin{quote}
`our individual subplans concerning our J-ing \emph{mesh} just in case there is some way we could J that would not violate either of our subplans but would, rather, involve the successful execution of those subplans' \citep[p.\ 106]{Bratman:1993je}.
\end{quote}
A natural generalisation is this:
\begin{quote}
our individual subplans concerning our <J$_1$, J$_2$>-ing \emph{mesh} just in case there is some way I could J$_1$ and you could J$_2$ that would not violate either of our subplans but would, rather, involve the successful execution of those subplans. 
\end{quote}
%
To illustrate, 
Ayesha's and Ahmed's subplans would fail to mesh if, in intending that they make the cross hit the red square,  Ayesha's plans had included pushing Ahmed out of the way and seizing his controls. 
They would also fail to mesh if Ayesha were planning to trick Ahmed into a situation where he would be unable to perform the actions he had been planning.
But in the case we have been describing, the agents' subplans mesh perfectly.
Each agent's subplans involve manipulating his or her own controls,
and the successes each seeks in doing this depends on the other successfully carrying out their subplans.
So Ayesha can rationally intend that they, Ayesha and Ahmed, make the cross hit the red square in accordance with and because of their intentions and meshing subplans of them.
And Ahmed likewise for making the cross hit the blue circle.

@@

In the situation just described,
Ayesha and Ahmed are playing a game and have different tasks.
Thanks to special features of the game environment, they both succeed by acting on an unshared intention.
Now compare two further players, Beatrice and Baldric, who are playing the same game. 
Their situations, knowledge states, intentions and actions are as similar as possible to Ayesha's and Ahmed's except for one detail.
Just by chance they have been assigned identical tasks: Beatrice's task is to make the cross hit the red square and Baldric's task is the same.
So where Ayesha and Ahmed have an unshared intention that they <J$_1$, J$_2$>,
Beatrice and Baldric meet Bratman's conditions (1)--(3) for having a shared intention that they J$_1$.  
But Beatrice, in planning and acting, does not rely on the coincidence of their intentions; and nor does Baldric.
(Beatrice relies on the fact Baldric intends that they J$_1$, of course; but she does not rely on the fact that Baldric intends what she intends.) 
Let us further stipulate that, due to an artefact of the way the game is structured,
the unshared intention and the 
	Bratman intention 
	\label{df:bratman_intention}
	(as we might label the structure of intention and knowledge 
	%specified in conditions (1)--(3) on page \pageref{quote:bratman_account}
	while leaving open whether it constitutes a shared intention) result in the two pairs performing same actions in the same way.
That is, Beatrice reasons about Baldric much as Ayesha reasons about Ahmed and Beatrice and does what Ayesha does; and likewise for Baldric and Ahmed.

We claim that Beatrice and Baldric have a shared intention that they J$_1$
only if 
Ayesha and Ahmed have a shared intention.%
\footnote{
Strictly speaking, 
	what matters for our argument is whether Ayesha and Ahmed have a shared intention \emph{in virtue of having the unshared intention that they <J$_1$, J$_2$>}.
	This is because, strictly speaking, we need to show, not that Beatrice and Baldric lack any shared intention whatsoever, but only that they lack a shared intention that they J$_1$ just in virtue of meeting Bratman's conditions (see (1)--(3) on page  \pageref{quote:bratman_account}). 
	For ease of exposition this is not made explicit in the main text.
} 
This claim follows from the similarities of the two cases.
The only difference is that Beatrice and Baldric happen to be assigned the same task, whereas Ayesha and Ahmed are not.
And neither Beatrice nor Baldric makes use of the fact that they have the same task. 
(This is not due to ignorance: it's just how they choose to approach their tasks.)
So if we consider  how  
		 Beatrice and Baldric's case
	differs from
		 that of Ayesha and Ahmed,
we can see that these differences do not plausibly amount to a difference with respect to shared agency.
Shared intention cannot feature in one case but not the other.

To show that Beatrice and Baldric do not have a shared intention it remains only to show that Ayesha and Ahmed do not have one. 
Here we must be careful.
First note that,
	 since Bratman provides only sufficient conditions for shared intention, 
	 his account doesn't tell us that an unshared intention is not a shared intention.
For all Bratman says, the conditions defining unshared intention might  be sufficient for shared intention.

But doesn't shared intention require at least this much,
that there be a single activity  about which each the agent involved has an intention? 
This might reasonably be doubted by those who, like Bratman, reject the Simple View according to which when an individual intentionally J-s she has an intention concerning her J-ing \citep{Bratman:1984jr}.
So 
	we shall not infer  that Ayesha and Ahmed lack a shared intention
	just because (by construction) there is no J such that Ayesha and Ahmed each intend that they, Ayesha and Ahmed, J.

Can we then appeal directly to intuition to show that Ayesha and Ahmed lack a shared intention?
Ayesha sees Ahmed's actions as constraints on her own, or else as opportunities.
She exploits Ahmed's intentions for her own ends.
Of course the situation is reciprocal: Ahmed exploits Ayesha in equal measure.
Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
and this is the full extent of their cooperation. 
We don't suppose that reciprocal exploitation is incompatible with shared intention. 
But Ayesha and Ahmed's interaction consists entirely in this sort reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.
Perhaps it is clear enough that 
the sort of shared agency that an account of shared intention is supposed to capture must involve more than this. 
If so, we can already claim that Ayesha and Ahmed are not acting on a shared intention.
But philosophers' intuitions about shared agency may vary, so it would be better if we could avoid such a blunt appeal to intuition.

How else could we support the claim that Beatrice and Baldric lack a shared intention? 
As mentioned at the start, 
the contrast cases are often used to anchor intuitions in theorising about shared agency.
In the next section we shall further support our claim by contrasting Beatrice and Baldric's case with a further case, one which is as similar as possible and which does seem to involve shared agency.
The fact that Beatrice and Baldric's case contrasts with this new case will support the claim that Beatrice and Baldric lack shared intention.
This is the aim of the following section.
A further motive for introducing this new contrast case is that it provides an indication concerning what is missing from Bratman's account, and so may help us to understand why his conditions are not sufficient for shared intention.

@@

First we need to introduce the notion of an agent-neutral plan.
We stipulate that a planning process, or a plan, is \emph{agent-neutral} just if it does not involve identifying any particular agents.  
This sort of planning is quite common.
For example, some housemates who have decided to make a pizza might sit down together to plan what needs doing without yet assigning roles to particular individuals. 
In so planning, each housemate is thinking about what is to be done and not what she herself will do.  
%(This is an idealisation, of course.)
At some point the housemates stop planning.
(This does not necessarily mean that they have a fully worked out plan; like any other plans, agent-neutral plans can have gaps that may need filling in later.)
They now divide up the roles.
Of course they may not find a way of dividing up roles that everyone is prepared to go along with---individuals' preferences, abilities and intentions may block the plan's adoption.
But suppose the housemates do divide up the roles in a way that is acceptable to everyone, 
	and that each implements her part in the plan.
Then each conceives of her own and the others' actions as part of single plan directed to achieving a single outcome.

In this example
	the housemates plan together and agree on a common plan.
	Planning together is plausibly an activity which involves shared agency.
	Note, however, that an individual can construct an agent-neutral plan by herself, even if its eventual execution will involve others. 
	In fact, two or more individuals who are assigned the same task and who will eventually collaborate might first each individually engage in agent-neutral planning.

Suppose, then, that our pizza-making housemates each individually devise an agent-neutral plan and come up with an assignment of agents to roles.  
What could ensure that their parallel planning results in identical plans?
(Strictly speaking it is not necessary for the plans and role assignments to be identical; it is enough if the resulting agent-specifying plans are, in a special sense, compatible.%
\footnote{
For an example of compatible plans, suppose that our task is to press a button simultaneously. 
If your plan is that each of us will to start to act in exactly 60 seconds whereas my plan specifies that you are the leader and we will start to act when you do, then our plans are compatible.
Consider also a case in which our task is to transport some apples and pears to a warehouse. 
My plan involves you taking care of the apples while I put the pears into the yellow crates and load them into the van through the side door.
If your plan involves me taking care of the pears while you put the apples into the green crates and load them into the van through the rear doors, our plans are compatible.
Here is one way to capture this intuitive notion of compatibility.
\label{fn:df_compatible}
Suppose that, for some outcome, two or more agents each have a plan for the realisation of that outcome. 
(These plans may, but need not, specify roles for all of the agents; but the plans must be agent-specific, not agent-neutral.)
By saying that these plans are \emph{compatible} we mean that:
(i) 
no agent would normally be prevented from performing the role she is assigned in her own plan by other agents performing the roles they are assigned in their plans;
and
(ii)
if all facts about which agents have which roles in which plans were common knowledge to the agents,
this would not affect the instrumental rationality of their each acting on the intention that they realise the outcome by performing the role she is assigned in her own plan.
%	each agent could rationally act on the intention that they realise the outcome by performing the role she is assigned in her own plan,
%	and she could do so even if all facts about which agents are performing which roles in which plans were common knowledge to the agents.
})
Communication but not necessary ***here

		The task demands and their planning strategies may conspire to ensure that they each come up with the same agent-neutral plan.
	The task demands and manifest properties of the agents, such as their distribution in space, may also ensure that each agent  assigns the same roles to the same individuals.

%
Finally, each agent may know enough about herself and the others to be able to determine, without communicating, whether the plan and role assignments will be acceptable to everyone. 
	And all of this---that they engage in parallel, agent-neutral planning resulting in identical (or compatible) plans and role assignments, which are acceptable to all---may be common knowledge to the agents.
	So it is possible, in principle at least, 
	that several agents might each individually engage in agent-neutral planning and rationally perform their part in the resulting plan, knowing that the others will do likewise.
	Parallel, agent-neutral planning can rationally result in coordinated action without presupposing shared agency.%
\footnote{
Note that we are claiming only that shared agency is not presupposed.
Our view is consistent with (but does not depend on) the claim
that
	if some agents each engage in parallel, agent-neutral planning and then rationally perform their part in the resulting plan,
	the upshot would be an exercise of shared agency.
}

Different perspectives are involved in
	forming a plan for  your own actions  only
and 
	forming a plan for  your own and others actions.
%\footnote{
%Perhaps it is impossible, strictly speaking, to plan others' actions. 
%In speaking loosely about planning your own and others actions, we mean the activity of constructing an agent-neutral plan and assigning roles as described above.
%}
  Of course, in planning your only your own actions, it may be necessary to consider how others' actions will affect, and be affected by, your won.
But in this case,  others' actions feature in your planning as constraints and opportunities.
By contrast, forming a plan for your own and others' actions 
	involves conceiving of your own and the others' actions as elements in a single plan directed to a single outcome.

@@

In short, then, Caitlin and Ciaran are like Beatrice and Baldric in nearly every respect. 
Each pair has a Bratman intention that they J$_1$,%
\footnote{
As stipulated above (see page \pageref*{df:bratman_intention}), 
two agents have a \emph{Bratman intention} that they J just if they meet conditions (1)--(3) on page \pageref{quote:bratman_account}.
}
%
 each pair acts on this intention and each pair ends up performing the same sequence of actions.
The difference is just that Beatrice and Baldric make no use of the fact that they are performing the same task.
	This fact does not feature in their planning. 
	Rather, each plans her own actions only and treats the other's actions as constraints to work around or opportunities to exploit.
By contrast, Caitlin and Ciaran embrace the fact that they are performing the same task. 
They may not like having to act together; in fact each may far prefer to act alone were that possible.
And, like Beatrice and Baldric, they are unconcerned with each other's success except insofar as their own success depends on it.
But Caitlin and Ciaran nevertheless make use of the fact that they have to perform a single task together by each constructing a single plan covering both of their actions and then carrying out their parts in these plans.
So why does Caitlin and Ciaran's case, but not Beatrice and Baldric's, plausibly involve shared agency?
The reason is  this:
	 at some stage of the planning which rationally guides and coordinates their actions,
	Caitlin and Ciaran each conceive of their actions as part of a single plan directed to achieving a single outcome.

Given the way Beatrice and Baldric's case contrasts with Caitlin and Ciaran's,
we conclude that Beatrice and Baldric do not have a shared intention.
But, by construction, 
 Beatrice and Baldric do meet Bratman's conditions for shared intention, and they do act appropriately on the corresponding intentions and knowledge. 
 So Beatrice and Baldric's case  is a counterexample to sufficiency of Bratman's conditions for shared intention.

In describing Caitlin and Ciaran we have not introduced contralateral commitments or any other element foreign to Bratman's account of shared agency. 
Our counterexample draws on the same planning resources Bratman's account draws on, with just one addition.
The addition is the idea that agents can conceive, or fail to conceive, of their actions as part of a single plan. 
In at least some cases, shared agency differs from individual agency in part because shared agency involves changing perspective so that one’s own and others' actions are conceived of as parts of a single plan.
